Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
new plots

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau7}
\end{center}
\caption{\textbf{Bimodality for RT and DS:} The triangles represent the Radiative
	Transfer and the lines represent the Doppler Shift.
	\label{fig:bimodality}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout5_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout25_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_bi_vout50_logtau7}
\end{center}
\caption{\textbf{Bimodality for RT and DS:} The triangles represent the Radiative
	Transfer and the lines represent the Doppler Shift.
	\label{fig:bimodality}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau5_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity.}
    Same layout as Figure \ref{fig:doppler_shift},
    this time  $\tauh=10^5$ and $\theta=90^\circ$.}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth]{./figures/results/doppler_shift_logtau7_theta90}
  \end{center}
  \caption{\textbf{Qualitative trends of changing outflow and
      rotational velocity.}
    Same layout as Figure \ref{fig:doppler_shift},
    this time  $\tauh=10^7$ and $\theta=90^\circ$.}
\end{figure}
